Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-20 paper_jasa.tex
difference of p-value to min.p-value figure added

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_loess_effect.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test. }
       \label{fig:power_screening}
\end{figure}

@@

@@

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_rank_counts12.pdf}
       \caption{Rank of p-values in a lineup of size 20 and the number of subjects choosing that plot in the lineup of experiment 1 and 2 with raw data (screening criteria 1). This indicates that most of the subjects pick the plot with minimum p-value (rank 1). There are subjects choosing the lineups with highest p-value(rank 20) but we can attribute this behavior to the type-I error. Can we?  \green{Maybe don't need this plot}}
       \label{fig:P-val_rank}
\end{figure*}

@@

This problem is further investigated in the paper \cite{waldo}.

@@

>>>>

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_loess_effect.pdf}}
       \caption{Observed power shown by loess smoother with simultaneous bootstrap confidence band and the power of conventional test. Responses are 1 and 0 depending on the success or failure respectively to identify the actual plot in the lineup. Size of the dots represents the number of responses for each lineup.}
       \label{fig:power_loess_effect}
\end{figure}

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_mixed.pdf}}
       \caption{The overall power estimated from model \ref{mixed} are shown. The corresponding power curve for conventional test is shown for comparison.}
       \label{fig:power_mixed}
\end{figure}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{power_mixed_subject.pdf}}
       \caption{Subject specific  power estimated from model \ref{mixed} are shown. The corresponding power curve for conventional test is shown for comparison.}
       \label{fig:power_mixed_subject}
\end{figure}

@@

%\begin{figure*}[hbtp]
%   \centering
%       \includegraphics[width=0.95\textwidth]{p_val_rank_counts12.pdf}
%       \caption{Rank of p-values in a lineup of size 20 and the number of subjects choosing that plot in the lineup of experiment 1 and 2 with raw data (screening criteria 1). This indicates that most of the subjects pick the plot with minimum p-value (rank 1). There are subjects choosing the lineups with highest p-value(rank 20) but we can attribute this behavior to the type-I error. Can we?  \green{Maybe don't need this plot}}
%       \label{fig:P-val_rank}
%\end{figure*}

@@

This problem is further investigated in the paper \cite{waldo}. \blue{Here is the plot in figure \ref{fig:pval_difference} as proposed.}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{pval_difference.pdf}}
       \caption{Difference between the data plot's $p$-value and the  smallest $p$ value of a null plot vs proportion correct.}
       \label{fig:pval_difference}
\end{figure}
